R Notebook

### 2021-12-13 Fish Data Analysis/Old Code.Rmd
Back before adding roup level features

---
title: "Fish Comparisons Simple Models"
output: html_notebook
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(car)
library(viridis)
library(boot)
```

So here we're going to do some simpler model selection things with the data using GLMs instead of GAMs

Sets up the functions that will be used later 
```{r}
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
ang_mean <- function(x){rad2deg(atan(mean(sin(deg2rad(x)))/mean(cos(deg2rad(x)))))}

fold_angle_0_360_to_0_180 <- function(x){abs(abs(x-180)-180)}
```

Reads in the data and alters it as needed 
```{r}
comp_data <- read.csv("Fish_Comp_Values.csv")
comp_data <- na.omit(comp_data)

comp_data <- comp_data %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Heading_Diff = abs(Heading_Diff)) %>%
                           filter(Distance <= 4) %>%
                           filter(Speed_Diff <= 6) %>% 
                           mutate(quarter_heading_diff = abs(abs(Heading_Diff-90)-90)) %>%
                           mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
                           mutate(Is_Reversed = ifelse(Heading_Diff > 150, 1, 0)) %>%
                           mutate(Angle = fold_angle_0_360_to_0_180(Angle))

sum_comp_data <- comp_data %>% mutate(X_Distance = round_any(X_Distance,0.25), 
                                      Y_Distance = round_any(abs(Y_Distance),0.25)) %>%
                               group_by(Flow,Ablation,Darkness,X_Distance,Y_Distance) %>%
                               summarise(Speed_Diff = mean(Speed_Diff),
                                         Heading_Diff = ang_mean(Heading_Diff),
                                         Sync = mean(Sync),
                                         Quarter_Heading_Diff = mean(quarter_heading_diff),
                                         Is_Aligned = mean(Is_Aligned),
                                         Is_Reversed = mean(Is_Reversed))

```

#Basic Stats

```{r}
speed_anova <- glm(Speed_Diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data)

Anova(speed_anova)

heading_anova <- glm(quarter_heading_diff ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data)

Anova(heading_anova)

sync_anova <- glm(Sync ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data)

Anova(sync_anova)

dist_anova <- glm(Distance ~ Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness, data = comp_data)

Anova(dist_anova)
```

```{r}
ggplot(comp_data, aes(x = Flow, y = Speed_Diff, fill = paste(Ablation,Darkness,sep="-")))+
  geom_boxplot(outlier.shape = NA) +
  ylim(0,3) +
  theme_light()

ggplot(comp_data, aes(x = Flow, y = quarter_heading_diff, fill = paste(Ablation,Darkness,sep="-")))+
  geom_boxplot(outlier.shape = NA) +
  ylim(0,90) +
  theme_light()

ggplot(comp_data, aes(x = Flow, y = Sync, fill = paste(Ablation,Darkness,sep="-")))+
  geom_boxplot(outlier.shape = NA) +
  ylim(0,1) +
  theme_light()

ggplot(comp_data, aes(x = Flow, y = Distance, fill = paste(Ablation,Darkness,sep="-")))+
  geom_boxplot(outlier.shape = NA) +
  ylim(0,4) +
  theme_light()
```

Now we add in distance and angle

```{r}
speed_anova_da <- glm(Speed_Diff ~ Distance*Angle*(Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness), data = comp_data)

Anova(speed_anova_da)

heading_anova_da <- glm(quarter_heading_diff ~ Distance*Angle*(Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness), data = comp_data)

Anova(heading_anova_da)

sync_anova_da <- glm(Sync ~ Distance*Angle*(Flow + Ablation + Darkness + Flow:Ablation + Flow:Darkness), data = comp_data)

Anova(sync_anova_da)
```

```{r}
ggplot(comp_data, aes(x = Distance, y = Speed_Diff, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
  facet_wrap(~ Flow) +
  theme_light()

ggplot(comp_data, aes(x = Distance, y = quarter_heading_diff, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
  facet_wrap(~ Flow) +
  theme_light()

ggplot(comp_data, aes(x = Distance, y = Sync, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
  facet_wrap(~ Flow) +
  theme_light()
```
```{r}
ggplot(comp_data, aes(x = Angle, y = Speed_Diff, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
  facet_wrap(~ Flow) +
  theme_light()

ggplot(comp_data, aes(x = Angle, y = quarter_heading_diff, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
  facet_wrap(~ Flow) +
  theme_light()

ggplot(comp_data, aes(x = Angle, y = Sync, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
  geom_smooth(method = "glm", formula = y ~ poly(x,4))+
  facet_wrap(~ Flow) +
  theme_light()
```

>>>>

---
title: "R Notebook"
output: html_notebook
---

```{r}
ggplot(comp_data, aes(x = Distance, y = Speed_Diff, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
  geom_smooth(method = "gam", formula = y ~ s(x))+
  facet_wrap(~ Flow) +
  theme_light()

ggplot(comp_data, aes(x = Distance, y = quarter_heading_diff, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
  geom_smooth(method = "gam", formula = y ~ s(x))+
  facet_wrap(~ Flow) +
  theme_light()

ggplot(comp_data, aes(x = Distance, y = Sync, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
  geom_smooth(method = "gam", formula = y ~ s(x))+
  facet_wrap(~ Flow) +
  theme_light()
```
```{r}
ggplot(comp_data, aes(x = Angle, y = Speed_Diff, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
  geom_smooth(method = "gam", formula = y ~ s(x))+
  facet_wrap(~ Flow) +
  theme_light()

ggplot(comp_data, aes(x = Angle, y = quarter_heading_diff, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
  geom_smooth(method = "gam", formula = y ~ s(x))+
  facet_wrap(~ Flow) +
  theme_light()

ggplot(comp_data, aes(x = Angle, y = Sync, color = paste(Ablation,Darkness,sep="-"), fill = paste(Ablation,Darkness,sep="-")))+
  geom_smooth(method = "gam", formula = y ~ s(x))+
  facet_wrap(~ Flow) +
  theme_light()
```
